\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
Fix

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science &
  tech folks are current and forward-looking, and it's consistent that we
  not be behind the leading edge.
  \item (b) You might say more how ACM needs to prepare itself in light of
  the trends that are coming -- carbon pricing is good organizational sense!
  There's some of this around ACM's potentially needing to adjust its
  business model, but it falls short of making a *business case for carbon
  pricing*, which is what I guess I'm recommending.
  \item Also, in addition to mentioning that Microsoft and other tech
  companies set a price on carbon, you might also note here that Exxon and
  other energy companies set an internal price on carbon as well, as a means
  of risk assessment. In other words, even the oil companies know what's
  coming.
  \end{itemize}
}

@@

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
  the right one? Link seems
  dead!  But Richard says ``As a reader, my first question is, how do I get
  access to this calculator? Can you cite this calculator in some way? It
  would be great to give a citation to where people can learn about it or
  use it, even if just, "To learn more about the calculator, e-mail
  _________."''}\fi. Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.

>>>>

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science and
  tech folks are current and forward-looking, and it's consistent that we
  not be behind the leading edge.
  \item (b) You might say more how ACM needs to prepare itself in light of
  the trends that are coming -- carbon pricing is good organizational sense!
  There's some of this around ACM's potentially needing to adjust its
  business model, but it falls short of making a *business case for carbon
  pricing*, which is what I guess I'm recommending.
  \item Also, in addition to mentioning that Microsoft and other tech
  companies set a price on carbon, you might also note here that Exxon and
  other energy companies set an internal price on carbon as well, as a means
  of risk assessment. In other words, even the oil companies know what's
  coming.
  \end{itemize}
}

@@

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
  the right one? Link seems
  dead!  But Richard says ``As a reader, my first question is, how do I get
  access to this calculator? Can you cite this calculator in some way? It
  would be great to give a citation to where people can learn about it or
  use it, even if just, "To learn more about the calculator, e-mail xxx."''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.
